### 2022-06-02 main/chapter_2ljets.tex
add split samples figure

Figure~\ref{fig:2ljets_low_crz_extensions}

@@

>>>>

Figure~\ref{fig:2ljets_low_crz_extensions}
Figure~\ref{fig:2ljets_splits}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_splits_met_Sign_CRZZ.png}
\caption{CR-VZ, diboson}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_splits_met_Sign_CRZ.png}
\caption{CR-Z, $\zjets$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_splits_met_Sign_CRtt.png}
\caption{CR-tt, rare top}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_splits_met_Sign_SRllbb.png}
\caption{SR-$\llbb$, rare top}
\end{subfigure}
\caption[
Subcomponents of diboson, $\zjets$ and rare top processes.
]{%
Subcomponents of (a) diboson, (b) $\zjets$ and (c, d) rare top processes.
Target samples broken down by simulated sample identity codes.
The `no filter' selection comprises $\zjets$ samples with unconstrained jet
flavour.
Errors are statistical.
}
\label{fig:2ljets_splits}
\end{figure}
